---
title: "Experimental composition PNJ1"
author: "Matt Crump"
date: 9/20/25
description: "notes to self"
comments:
  giscus: 
    repo: CrumpLab/crumplab_comments
categories: 
  - piano
  - Ableton
  - experimental 
  - composition
execute: 
  echo: true
  message: false
  warning: false
  eval: false
format:
  html:
    code-fold: true
lightbox: 
  match: auto
  desc-position: right
  loop: true
---

```{r}

```


```{r}
#| echo: false
#| eval: true

html_tag_audio <- function(file, type = c("wav")) {
  type <- match.arg(type)
  htmltools::tags$audio(
    controls = "",
    htmltools::tags$source(
      src = file,
      type = glue::glue("audio/{type}", type = type)
    )
  )
}

```

Played dissonant free form piano.

Went over the first two minutes one phrase at a time and added a voice part, which was an attempt to minimally summarize what was going on in the phrase.

Went over again adding a bass part one phrase at a time.

Popped everything into Ableton. Converted the piano tracks to midi. Mixed the piano parts together with a few synth sounds from the Artemis.

Experimental PNJ1:

`r html_tag_audio("PNJ1.mp3", type = "wav")`




