---
title: "RL4"
author: "Matt Crump"
date: 9/16/25
description: "notes to self"
comments:
  giscus: 
    repo: CrumpLab/crumplab_comments
categories: 
  - tracker
  - m8
  - ableton
  - composition
execute: 
  echo: true
  message: false
  warning: false
  eval: false
format:
  html:
    code-fold: true
lightbox: 
  match: auto
  desc-position: right
  loop: true
---

```{r}

```


```{r}
#| echo: false
#| eval: true

html_tag_audio <- function(file, type = c("wav")) {
  type <- match.arg(type)
  htmltools::tags$audio(
    controls = "",
    htmltools::tags$source(
      src = file,
      type = glue::glue("audio/{type}", type = type)
    )
  )
}

```

The weekend:

Working off of this drum beat, courtesy of Ramsey Lewis. 

`r html_tag_audio("RL_IYGI931.wav", type = "wav")`

Added a bass line and rhodes chords. Jammed over them with rhodes, guitar, osmose and artemis. Ended up with lots of material there. Cut it down to a simple back and forth between guitar and rhodes, plus a few tidbits.

`r html_tag_audio("RL4_take_1.mp3", type = "wav")`

----------------

Monday:

Used the above as a backing track, added lots of piano leads over top. 

----------------

Tuesday morning:

Try stitching something together.

----------------

It's saturday now, did a bunch of stuff on this one, the third take is:

`r html_tag_audio("RL4_take_3.mp3", type = "wav")`




