---
title: "Ep-133 trial runs"
author: "Matt Crump"
date: 9/21/25
description: "notes to self"
comments:
  giscus: 
    repo: CrumpLab/crumplab_comments
categories: 
  - ep-133
execute: 
  echo: true
  message: false
  warning: false
  eval: false
format:
  html:
    code-fold: true
lightbox: 
  match: auto
  desc-position: right
  loop: true
---

```{r}

```


```{r}
#| echo: false
#| eval: true

html_tag_audio <- function(file, type = c("wav")) {
  type <- match.arg(type)
  htmltools::tags$audio(
    controls = "",
    htmltools::tags$source(
      src = file,
      type = glue::glue("audio/{type}", type = type)
    )
  )
}

```

Putting some time into the EP-133. Really fun for immediate finger drumming. It's been a while since I picked up the EP-133, and I forgot all of the details for programming it. I doubt I will ever remember those details, le grand sigh. That's an understatement about my doubt, which is more like certainty.

It is really fun to use though, and short snappy beats can fall out of it fairly easily. I don't trust my ears and headphones to set levels etc. for mastering, so will probably start recording into the m8 during the creation process to keep everything separate before final mixing.

`r html_tag_audio("KOCOMP1.mp3", type = "wav")`

`r html_tag_audio("KOCOMP2.mp3", type = "wav")`




